\documentclass{article}
\usepackage{blindtext}
\usepackage{amsmath}
%usepackage{indentfirst}
\usepackage[colorlinks = true,
linkcolor = blue,
urlcolor  = blue,
citecolor = blue,
anchorcolor = blue]{hyperref}

 
\title{TAMS Calculus III/Linear Algebra Syllabus}
\author{TAS Academic Committee\\Simon Xiang}
\date{\today}
\begin{document}
 
\maketitle

\section*{General Information}

Welcome to the syllabus page for the 2019-2020 TAS Higher Math Committee!
Information that will be covered include structure of review sessions, tutoring sessions, budgeting,
and resources that will be made available. 

\section*{Review Sessions}

\subsection*{What a review session will look like}

Review sessions will serve as opportunities for students to review material learned in class.
Reviews will be pretty evenly split between learning material\slash gaining intuition and 
working problems. Computationally, Calculus III and Linear Algebra are not difficult subjects, 
however I noticed my peers struggling to solve some problems because they didn't know how to 
approach or visualize them, which is why I'll focus on building intuition first and then learning
how to work problems afterward.

\subsection*{When reviews will occur}

Unfortunately, not everyone can take Dr.~Tran for Linear Algebra, and as a result many TAMS
kids find themselves in various Calculus III or Linear Algebra classes. After obtaining the syllabi from the
more ``popular'' professors, I will try to hold reviews that will benefit the most people before 
tests. 

For example:

\begin{itemize}
    \item There are 50 kids in Dr.~Tran's class.
    \item There are 20 kids in Dr.~Widmer's class (poor kids).
    \item Dr.~Tran's first test will be sometime late-October.
    \item Dr.~Widmer's first test will be early-November.
    \item Therefore I will hold the review covering all the content from both Dr. Tran's and Dr.~Widmer's %
    first tests mid-October, since Dr.~Widmer's test is sufficiently close so that hopefully the kids who %
    attended won't forget everything.
\end{itemize}

\section*{Resources}

\subsection*{Videos}
Here are some video (series) that I've found that may be of use, I've put an asterisk by the 
ones I personally used to learn the subjects.

\begin{itemize}
    \item \href{https://www.youtube.com/watch?v=fNk_zzaMoSs&list=PLZHQObOWTQDPD3MizzM2xVFitgF8hE_ab}%
    {3Blue1Brown's \textit{Essence of Linear Algebra} Series (15 videos)*}
    \item \href{https://ocw.mit.edu/courses/mathematics/18-06-linear-algebra-spring-2010/video-lectures/}{MIT %
    OCW's Video Lectures on Linear Algebra (34 videos)}
    \item \href{https://www.khanacademy.org/math/multivariable-calculus}{Khan Academy's Multivariable Calculus %
    Videos (a lot of videos)*}
    \item \href{https://www.youtube.com/playlist?list=PLDesaqWTN6ESk16YRmzuJ8f6-rnuy0Ry7}{Professor Leonard's %
    Calculus III Videos (34 videos)}
\end{itemize}

\subsection*{Reading}

These are the ``standard'' textbooks that the classes should use.

\begin{itemize}
    \item Linear Algebra and Its Applications, 5th Edition
    \item Calculus: Early Transcendentals
\end{itemize}

On another side note, I'm planning on typing up formula\slash review sheets in \LaTeX{}
similar to this syllabus before tests and such. I don't know if I'll be able to make one
before every test, but I'll try my best.

\subsection*{Practice}

The best way to learn math is to do math. Practice 
resources I'll try to make available include:

\begin{itemize}
    \item Previous Calculus III exams (Biswas)
    \item Previous Linear Algebra exams (Tran)
    \item Worked Weekly Quizzes (Tran)
    \item Worked solutions to difficult homework questions
    \item Anything else I can find
\end{itemize}

\section*{Budget}
Not needed.

\end{document}

