\documentclass{article}
\usepackage{amsmath, amssymb, amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{question}{Question}
\renewcommand\qedsymbol{$\boxtimes$}
\begin{document}
\section*{Chapter 4}
\begin{question}
    Let $a,b \in \mathbb{Z}.$ Show that $4 \mid a^2-b^2$ iff $a$ and $b$ have the same parity.
\end{question}
\begin{proof}
    Assume that $4 \mid a^2 - b^2$, then $a^2-b^2=4n$ for some $n \in \mathbb{Z}$, so $(a+b)(a-b)=4n.$ If $a$ and $b$ had opposite parity, then both $(a+b)$ and $(a-b)$ would be odd, and so $(a+b)(a-b)$ would also be odd. However, $4n=2(2n),$ and since $2n \in \mathbb{Z},$ $4n$ is even. We conclude that $a$ and $b$ must have the same parity.

    Conversely, assume that $a$ and $b$ have the same parity.

    \textbf{Case 1:} $a$ and $b$ are even. Then $a=2n$ and $b=2m$ for some $n,m \in \mathbb{Z}.$ So $a^2-b^2 = 4n^2-4m^2 = 4(n^2-m^2).$ Since $n^2-m^2 \in \mathbb{Z},$ $4 \mid a^2-b^2.$

    \textbf{Case 2:} Now assume both $a$ and $b$ are odd. Then $a=2n+1$ and $b=2m+1$ for some $n,m \in \mathbb{Z}$. So $a^2-b^2=(2n+1)^2-(2m+1)^2=(4n^2+4n+1)-(4m^2+4m+1)=4n^2+4n-4m^2-4m=4(n^2+n-m^2-m).$ Now $\mathbb{Z}$ is closed under multiplication and addition, so $n^2+n-m^2-m \in \mathbb{Z}$ if $n,m \in \mathbb{Z}$. This means we can write $a^2-b^2$ in the form $4k$ where $k \in \mathbb{Z}$, and we conclude that $4 \mid a^2-b^2.$
\end{proof}
\begin{question}
    Let $a \in \mathbb{Z}$. Show that $3 \mid a$ iff $3 \mid a^2$.
\end{question}
\begin{proof}
    Assume $3 \mid a.$ Then $a=3n$ for some $n \in \mathbb{Z}$, so $a^2=(3n)^2=9n^2=3(3n^2)$. Since $3n^2 \in \mathbb{Z}$, we have $3 \mid a^2.$ 
    
    Conversely, assume that $3 \mid a^2$ and $3 \nmid a$ by contradiction. Then $a^2=3n$ for some $n\in\mathbb{Z}$, and either $a=3k+1$ or $a=3k+2$ for some $k\in\mathbb{Z}$.

    \textbf{Case 1:} $a=3k+1$ for some $k\in\mathbb{Z}$. Then $a^2=(3k+1)^2=9k^2+6k+1=3(3k^2+2k)+1.$ Since $\mathbb{Z}$ is closed under multiplication and addition, we have $3k^2+2k \in \mathbb{Z}.$ So $a^2$ is of the form $3m+1$ for some $m \in \mathbb{Z}$, which is a contradiction since $3 \mid a^2.$

    \textbf{Case 2:} $a=3k+2$ for some $k \in \mathbb{Z}.$ It follows that $a^2=(3k+2)^2=9k^2+12k+4=3(3k^2+6k+1)+1.$ Since $3k^2+6k+1$ is an integer, $a^2$ is of the form $3m+1$ for some $m \in \mathbb{Z}$, a contradiction. We conclude that $3 \mid a.$
\end{proof}
\begin{question}
    Use the result from Question 2 to show that $\sqrt3$ is irrational.
\end{question}
\begin{proof}
    We prove the desired result by contradiction. Assume $\sqrt3$ is rational, that is, it can be expressed in the form $\frac{m}{n}$ where $m,n \in \mathbb{Q}$, $n \neq 0,$ and $m$ and $n$ are in lowest terms. Then $m=\sqrt3n$ which implies $m^2=3n^2$, which subsequently implies that $3 \mid m^2.$ But then $3 \mid m$ by our previous result, and so $m=3k$ for some $k \in \mathbb{Z}$. Therefore $3n^2=(3k)^2=9k^2$, which implies that $n^2 = 3k^2$ which leads to the fact that $3 \mid n^2.$ However, this implies $3 \mid n$ by our previous result, a contradiction since we assumed that $m$ and $n$ had no common divisors. Therefore $\sqrt3$ is irrational.
\end{proof}
\begin{question}
    Let $a,b \in \mathbb{R}.$ Show that if $a+b$ is rational, then $a$ is irrational or $b$ is irrational.
\end{question}
\begin{proof}
    Assume by the contrapositive statement that $a$ is rational and $b$ is irrational. We want to show that $a+b$ is not rational— we do this by contradiction. Assume that $a+b \in \mathbb{Q},$ then $a+b=\frac{m}{n}$ for some $m,n \in \mathbb{Z}.$ We have $a=\frac{k}{q}$ by assumption. So 
    \[b=\frac{m}{n}-a=\frac{m}{n}-\frac{k}{q}=\frac{mq+nk}{nq}\]
which is rational since $\mathbb{Q}$ is a field. But $b$ is irrational by assumption, a contradiction, and we are done. 
\end{proof}
\end{document}
